Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-02-05 ICML-submission/introduction.tex
a pass over the paper

\begin{protocol}[h]
\caption{\textsc{Online Multiclass Linear Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$. \\
\For{$t=1,2,\dots,T$}{
Adversary chooses example $(x_t, y_t) \in V \times \{1,2,\dots,K\}$ where $x_t$ is revealed to the learner.\\
Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
Observe feedback $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
}
\end{protocol}

@@

In the full-information feedback setting, it is well known
\citep{Crammer-Singer-2003} that if all examples have norm at most $R$ and are
weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes. It
is also known that any (possibly randomized) algorithm must make $\frac{1}{2}
\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. The
\textsc{Multiclass Perceptron} achieves an information-theoretically optimal
mistake bound, while being computationally and memory efficient.~\footnote{For
completeness, we present these folklore results along with their proofs in
Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
material.}

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best of our knowledge,
it is not known how to design an efficient algorithm with a finite mistake bound
before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
claimed that their Conservative OVA algorithm with PA-I update has a finite
mistake bound under the strong linear separability condition, their
Theorem 2 is incorrect: first, their Lemma 1 (with $C = +\infty$) along with Theorem 1
implies a mistake upper bound of
$(\frac{R}{\gamma})^2$, which contradicts our lower
bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
second, their Lemma 1 cannot be directly applied to the bandit setting, as the
algorithm only makes updates on a subset of the $w_i$'s.} We design a simple and
efficient algorithm
(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
that makes at most $O(K (R/\gamma)^2)$ mistakes in expectation. Its memory
complexity and per-round time complexity are both $O(dK)$. The algorithm can be
viewed as running $K$ copies of the \textsc{Binary Perceptron} algorithm, one
copy for each class. We prove that any (possibly randomized) algorithm must make
$\Omega(K (R/\gamma)^2)$ mistakes in the worst case. The extra $O(K)$
multiplicative factor in the mistake bound, as compared to the full-information
setting, is the price we pay for the bandit feedback, or more precisely, the
lack of full-information feedback.

@@

The resulting kernelized algorithm runs in time polynomial in the
original dimension of the feature vectors $d$, the number of classes $K$, and
the number of rounds $T$. We prove that if the examples lie in the unit ball of
$\R^d$ and are weakly linearly separable with margin $\gamma$,
Algorithm~\ref{algorithm:kernelized} makes at
most $2^{\widetilde{O}(\min(K \log^2 (1/\gamma), \sqrt{1/\gamma}
\log K))}$ mistakes.

>>>>

\begin{protocol}[h]
\caption{\textsc{Online Multiclass Linear Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$. \\
\For{$t=1,2,\dots,T$}{
Adversary chooses example $(x_t, y_t) \in V \times \{1,2,\dots,K\}$ where $x_t$ is revealed to the learner.\\
Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
Observe feedback $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$.
}
\end{protocol}

@@

In the full-information feedback setting, it is well known
\citep{Crammer-Singer-2003} that if all examples have norm at most $R$ and are
weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes. It
is also known that any (possibly randomized) algorithm must make $\frac{1}{2}
\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. The
\textsc{Multiclass Perceptron} achieves an information-theoretically optimal
mistake bound, while being time and memory efficient.~\footnote{For
completeness, we present these folklore results along with their proofs in
Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
material.}

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best of our knowledge,
it is not known how to design an efficient algorithm with a finite mistake bound
before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
claimed that their Conservative OVA algorithm with PA-I update has a finite
mistake bound under the strong linear separability condition, their
Theorem~2 is incorrect: first, their Lemma~1 (with $C = +\infty$) along with their Theorem~1
implies a mistake upper bound of
$(\frac{R}{\gamma})^2$, which contradicts the lower
bound in our Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
second, their Lemma~1 cannot be directly applied to the bandit feedback setting.}
We design a simple and
efficient algorithm
(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
that makes at most $O(K (R/\gamma)^2)$ mistakes in expectation. Its memory
complexity and per-round time complexity are both $O(dK)$. The algorithm can be
viewed as running $K$ copies of the \textsc{Binary Perceptron} algorithm, one
copy for each class. We prove that any (possibly randomized) algorithm must make
$\Omega(K (R/\gamma)^2)$ mistakes in the worst case. The extra $O(K)$
multiplicative factor in the mistake bound, as compared to the full-information
setting, is the price we pay for the bandit feedback, or more precisely, the
lack of full-information feedback.

@@

The resulting kernelized algorithm runs in time polynomial in the
original dimension of the feature vectors $d$, the number of classes $K$, and
the number of rounds $T$. We prove that if the examples lie in the unit ball of
$\R^d$ and are weakly linearly separable with margin $\gamma$,
Algorithm~\ref{algorithm:kernelized} makes at
most $\min (2^{\widetilde{O}(K \log^2
(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$ mistakes.

### 2019-02-05 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
a pass over the paper

In this section, we prove a mistake lower bound for a family of algorithms
called \textit{ignorant algorithms}. Ignorant algorithms ignore the examples on
which they make mistakes. This assumption seems strong, but as we will explain
below, it is actually natural, and several recently proposed bandit
classification algorithms that achieve $\sqrt{T}$ regret bounds belong to this
family, e.g., SOBA~\citep{Beygelzimer-Orabona-Zhang-2017},
OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}. Also,
\textsc{Nearest-Neighbor Algorithm} (Algorithm~\ref{algorithm:nearest-neighbor})
presented in Appendix~\ref{section:nearest-neighbor-algorithm} is an ignorant
algorithm.

@@

\begin{proof}
We consider the strategy for the adversary described in
Algorithm~\ref{algorithm:adversary-strategy}.

@@

In rounds $1,2,\dots,\tau-1$, the algorithm predicts the incorrect class $2$
with probability at least $q_0$. Thus,
$$
\Exp\left[\sum_{t=1}^{\tau - 1} \indicator{\widehat y_t\neq y_t}\right] = q_0 \Exp[\tau] \; .
$$
In rounds $\tau, \tau+1, \dots, T$, all the examples are the same and are equal
to $(v_\tau, 2)$. Let $s$ be the first time step $t$ such that $t \ge \tau$
and the algorithm makes a correct prediction. If the algorithm makes mistakes
in all rounds $\tau, \tau+1, \dots, T$, we define $s = T+1$.
By definition the algorithm makes mistakes in rounds $\tau, \tau+1, \dots, s-1$
Then,
$$
\Exp\left[\sum_{t=\tau}^T \indicator{\widehat y_t\neq y_t}\right] \ge \Exp[s-\tau].
$$
Since the algorithm is ignorant, conditioned on $\tau$, the random variable $s-\tau$
has a truncated geometric distribution with parameter $p_\tau(2|v_\tau) \le q_0$.
Therefore,
$$
\Exp[s-\tau ~|~ \tau]
\ge
\Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \; .
$$

Combining the two, we have that
\begin{align*}
& \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
& \ge q_0 \Exp[\tau] + \Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-T_1+1}\right)\right] \\
& =  \Exp \left[ \Exp \left[ q_0 \tau + \frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \right] \; .
\end{align*}
We lower bound the last expression by considering two cases for $\tau$.
If $\tau \ge \frac{1}{2}T + 1$, then the last expression is lower bounded by
$\frac{1}{2}q_0 T = \frac{1}{2} \sqrt{T}$. If
$\tau < \frac{1}{2}T+1$, it is lower bounded by
\begin{align*}
& \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2}T}\right) \\
& = \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2q_0^2}}\right) \\
& \ge \frac{1-\frac{1}{\sqrt{2}}}{q_0}\left(1-\frac{1}{\sqrt{e}}\right) \\
& \ge \frac{1}{10} \sqrt{T} \; .
\end{align*}

Observe that in phase 1, the labels are equal to $1$ and in phase 2 the labels
are equal to $2$. Note that $(x_\tau, y_\tau)=(x_{\tau+1}, y_{\tau+1})= \dots =
(x_T, y_T) = (v_\tau, 2)$. Consider the vectors $u_1, u_2, \dots, u_N$ as
defined in Lemma~\ref{lemma:embed_d_gamma} We claim that $w_1=-u_\tau/2$ and
$w_2=u_\tau/2$ satisfy the conditions of strong linear separabaility.

Clearly $\norm{w_1}^2 + \norm{w_2}^2 \le (\norm{w_1} + \norm{w_2})^2 \le
(\frac{1}{2} + \frac{1}{2})^2 \le 1$. By Lemma~\ref{lemma:embed_d_gamma}, we
have $\ip{w_2/2}{x_t} = \ip{u_\tau/2}{v_\tau} \ge \gamma/2, \forall t \ge \tau$ and
$\ip{w_2/2}{x_t} = \ip{u_\tau/2}{v_t} \le - \gamma/2$ for all $t < \tau$. Similarly,
$\ip{w_1/2}{x_t} \le -\gamma/2$ for all $t \ge \tau$ and $\ip{w_1/2}{x_t} \ge
\gamma/2$ for all $t < \tau$. Thus, the examples are strongly separable with margin
$\gamma$.
\end{proof}

>>>>

In this section, we prove a mistake lower bound for a family of algorithms
called \textit{ignorant algorithms}. Ignorant algorithms ignore the examples on
which they make mistakes. This assumption seems strong, but as we will explain
below, it is actually natural, and several recently proposed bandit linear
classification algorithms that achieve $\sqrt{T}$ regret bounds belong to this
family, e.g., SOBA~\citep{Beygelzimer-Orabona-Zhang-2017},
OBAMA~\citep{Foster-Kale-Luo-Mohri-Sridharan-2018}. Also,
\textsc{Nearest-Neighbor Algorithm} (Algorithm~\ref{algorithm:nearest-neighbor})
presented in Appendix~\ref{section:nearest-neighbor-algorithm} is an ignorant
algorithm.

@@

\begin{proof}[Proof of \autoref{theorem:ignorant-lower-bound}]
We consider the strategy for the adversary described in
Algorithm~\ref{algorithm:adversary-strategy}.

@@

In rounds $1,2,\dots,\tau-1$, the algorithm predicts the incorrect class $2$
with probability at least $q_0$. Thus,
$$
\Exp\left[\sum_{t=1}^{\tau - 1} \indicator{\widehat y_t\neq y_t}\right] = q_0 \Exp[(\tau - 1)] \; .
$$
In rounds $\tau, \tau+1, \dots, T$, all the examples are the same and are equal
to $(v_\tau, 2)$. Let $s$ be the first time step $t$ such that $t \ge \tau$
and the algorithm makes a correct prediction. If the algorithm makes mistakes
in all rounds $\tau, \tau+1, \dots, T$, we define $s = T+1$.
By definition the algorithm makes mistakes in rounds $\tau, \tau+1, \dots, s-1$.
Therefore,
$$
\Exp\left[\sum_{t=\tau}^T \indicator{\widehat y_t\neq y_t}\right] \ge \Exp[s-\tau].
$$
Since the algorithm is ignorant, conditioned on $\tau$, the random variable $s-\tau$
has a truncated geometric distribution with parameter $p_\tau(2|v_\tau) \le q_0$.
Therefore,
$$
\Exp[s-\tau ~|~ \tau]
\ge
\Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \; .
$$

Combining the two, we have that
\begin{align*}
& \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
& \ge q_0 \Exp[\tau - 1] + \Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right)\right] \\
& =  \Exp \left[ \Exp \left[ q_0 (\tau - 1) + \frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \right] \; .
\end{align*}
We lower bound the last expression by considering two cases for $\tau$.
If $\tau \ge \frac{1}{2}T + 1$, then the last expression is lower bounded by
$\frac{1}{2}q_0 T = \frac{1}{2} \sqrt{T}$. If
$\tau < \frac{1}{2}T+1$, it is lower bounded by
\begin{align*}
& \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2}T}\right) \\
& = \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2q_0^2}}\right) \\
& \ge \frac{1-\frac{1}{\sqrt{2}}}{q_0}\left(1-\frac{1}{\sqrt{e}}\right) \\
& \ge \frac{1}{10} \sqrt{T} \; .
\end{align*}

Observe that in phase 1, the labels are equal to $1$ and in phase 2 the labels
are equal to $2$. Note that $(x_\tau, y_\tau)=(x_{\tau+1}, y_{\tau+1})= \dots =
(x_T, y_T) = (v_\tau, 2)$. Consider the vectors $u_1, u_2, \dots, u_N$ as
defined in Lemma~\ref{lemma:embed_d_gamma} We claim that $w_1=-u_\tau/2$ and
$w_2=u_\tau/2$ satisfy the conditions of strong linear separability.

Clearly $\norm{w_1}^2 + \norm{w_2}^2 \le (\norm{w_1} + \norm{w_2})^2 \le
(\frac{1}{2} + \frac{1}{2})^2 \le 1$. By Lemma~\ref{lemma:embed_d_gamma}, we
have $\ip{w_2/2}{x_t} = \ip{u_\tau/2}{v_\tau} \ge \gamma/2, \forall t \ge \tau$ and
$\ip{w_2/2}{x_t} = \ip{u_\tau/2}{v_t} \le - \gamma/2$ for all $t < \tau$. Similarly,
$\ip{w_1/2}{x_t} \le -\gamma/2$ for all $t \ge \tau$ and $\ip{w_1/2}{x_t} \ge
\gamma/2$ for all $t < \tau$. Thus, the examples are strongly linearly
separable with margin $\gamma$.
\end{proof}

### 2019-02-05 ICML-submission/np-hardness-of-the-weak-labeling-problem.tex
a pass over the paper

The hardness proof is based on a reduction from the set splitting problem, which
is proven to be NP-complete by Lovasz \cite{Garey-Johnson-1979}, to our weak
labeling problem. The reduction is adapted from \cite{Blum-Rivest-1993}.
\begin{figure}[H]
\begin{framed}
\begin{center}
    \textbf{Set Splitting}
\end{center}
\textbf{Given:} A finite set $S$ and a collection $C$ of subsets $c_i$ of $S$. \\
\textbf{Question:} Do there exist disjoint sets $S_1$ and $S_2$ such that $S_1 \cup S_2 = S$ and $\forall i, c_i\not\subseteq S_1$ or $c_i\not\subseteq S_2$?
\end{framed}
\end{figure}

@@

Now we show $\forall j$, $c_j \not\subset S_1$ and $c_j \not\subset S_2$ by
contraction. Assume there exists some $j$ such that $c_j \subset S_1$. By our
definition of $S_1$, we have $\ip{w_1-w_3}{(\e_i, 1)} > 0$ for all $i\in c_j$.
Therefore,
\begin{align*}
\sum_{i\in c_j} \ip{w_1-w_3}{\left(\e_i, 1\right)}
& = \ip{w_1-w_3}{\left(\sum_{i\in c_j} \e_i, |c_j|\right)}  \\
& > 0.
\end{align*}
Because Type 1 sample has label $3$, we also have
$$
\ip{w_1-w_3}{\left(\zero, 1\right)} < 0.
$$
Combining the above two inequalities, we get
\begin{align*}
& \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, 1\right)} \\
& = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)}  \\
& \qquad - (|c_j|-1)\ip{w_1-w_3}{\left(\zero, 1\right)} \\
& > 0 \; .
\end{align*}
Note that $\left(\sum_{i\in c_j}\e_i, 1\right)$ is a feature vector for Type 3
samples. Thus the above inequality contradicts that Type 3 samples have label 3.
Therefore, $c_j \not\subset S_1$. If we assume there exists some $c_j \subset
S_2$, same arguments apply and also lead to contradiction.
\end{proof}

>>>>

The hardness proof is based on a reduction from the set splitting problem, which
is proven to be NP-complete by Lov\'asz \cite{Garey-Johnson-1979}, to our weak
labeling problem. The reduction is adapted from \cite{Blum-Rivest-1993}.
\begin{figure}[H]
\begin{framed}
\begin{center}
    \textbf{Set Splitting}
\end{center}
\textbf{Given:} A finite set $S$ and a collection $C$ of subsets $c_i$ of $S$. \\
\textbf{Question:} Do there exist disjoint sets $S_1$ and $S_2$ such that $S_1 \cup S_2 = S$ and $\forall i, c_i\not\subseteq S_1$ and $c_i\not\subseteq S_2$?
\end{framed}
\end{figure}

@@

Now we show $\forall j$, $c_j \not\subset S_1$ and $c_j \not\subset S_2$ by
contradiction. Assume there exists some $j$ such that $c_j \subset S_1$. By our
definition of $S_1$, we have $\ip{w_1-w_3}{(\e_i, 1)} > 0$ for all $i\in c_j$.
Therefore,
\begin{align*}
\sum_{i\in c_j} \ip{w_1-w_3}{\left(\e_i, 1\right)}
& = \ip{w_1-w_3}{\left(\sum_{i\in c_j} \e_i, |c_j|\right)}  \\
& > 0.
\end{align*}
Because Type 1 sample has label $3$, we also have
$$
\ip{w_1-w_3}{\left(\zero, 1\right)} < 0.
$$
Combining the above two inequalities, we get
\begin{align*}
& \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, 1\right)} \\
& = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)}  \\
& \qquad - (|c_j|-1)\ip{w_1-w_3}{\left(\zero, 1\right)} \\
& > 0 \; .
\end{align*}
Note that $\left(\sum_{i\in c_j}\e_i, 1\right)$ is a feature vector for Type 3
samples. Thus the above inequality contradicts that Type 3 samples have label 3.
Therefore, $c_j \not\subset S_1$. If we assume there exists some $c_j \subset
S_2$, same arguments apply and also lead to contradiction.
\end{proof}

### 2019-02-05 ICML-submission/related-work.tex
a pass over the paper

The problem considered here is a special case of the
contextual bandit problem~\citep{Auer-2003, Langford-Zhang-2008}. 
In this general problem, there is a hidden cost vector $c_t$ associated with every prediction in round $t$.  Upon receiving $x_t$ and predicting $\widehat{y}_t \in \{1,\ldots,K\}$, the learner gets to observe the incurred cost $c_t(\widehat{y}_t)$.  
The goal of the learner is to minimize its regret with respect to the best predictor in some predefined policy class $\Pi$, given by $\sum_{t=1}^T c_t(\widehat{y}_t) -
\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
Bandit multiclass learning is a special case
where the cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$ and 
the policy class is the set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
There has been significant progress on the general contextual bandit problem
assuming access to an optimization oracle that returns a policy in $\Pi$ with the smallest total cost on any given set of cost-sensitive examples~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
Syrgkanis-Krishnamurthy-Schapire-2016,
Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
While solving a more general problem without making assumptions on the structure of the cost vector $c_t$ or the policy class, these results assume that $x_t$ vectors or $(x_t,c_t)$ pairs are generated i.i.d. and that such an oracle abstracting efficient search through $\Pi$ is available---neither of which we assume here.

%However, these algorithms are not
%truly computationally efficient in our setting, as it is NP-hard in general to
%find a linear classifier that minimizes the empirical cost over a set of
%examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.

Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
contextual bandits with surrogate losses, focusing on regrets of the form
$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K}
\sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$, where $\calF$ contains score functions
$f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac
s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
information-theoretic regret upper bounds for various settings of $\calF$. On
the other hand, it gives an efficient algorithm with an $O(\sqrt{T})$ regret
against the benchmark of $\calF = \cbr{x \mapsto W x: W \in \R^{k \times d},
\one^T W = 0}$. A direct application of this result to \textsc{Online Bandit
Multiclass Linear Classification} gives an algorithm with $O(\sqrt{T})$ mistake
bound in the strongly linearly separable case.

>>>>

The problem considered here is a special case of the
contextual bandit problem~\citep{Auer-2003, Langford-Zhang-2008}.
In this general problem, there is a hidden cost vector $c_t$ associated with every prediction in round $t$.  Upon receiving $x_t$ and predicting $\widehat{y}_t \in \{1,\ldots,K\}$, the learner gets to observe the incurred cost $c_t(\widehat{y}_t)$.
The goal of the learner is to minimize its regret with respect to the best predictor in some predefined policy class $\Pi$, given by $\sum_{t=1}^T c_t(\widehat{y}_t) -
\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
Bandit multiclass learning is a special case
where the cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$ and
the policy class is the set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
There has been significant progress on the general contextual bandit problem
assuming access to an optimization oracle that returns a policy in $\Pi$ with the smallest total cost on any given set of cost-sensitive examples~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
Syrgkanis-Krishnamurthy-Schapire-2016,
Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
However, such an oracle abstracting efficient search through $\Pi$ is generally not available
in our setting due to computational hardness results~\citep{Arora-Babai-Stern-Sweedyk-1997}.

%While solving a more general problem without making assumptions on the structure of the cost vector $c_t$ or the policy class, these results assume that $x_t$ vectors or $(x_t,c_t)$ pairs are generated i.i.d. and that such an oracle abstracting efficient search through $\Pi$ is available---neither of which we assume here.

%While solving a more general problem without making assumptions on the structure of the cost vector $c_t$ or the policy class,
%However, these algorithms are not
%truly computationally efficient in our setting, as it is NP-hard in general to
%find a linear classifier that minimizes the empirical cost over a set of
%examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.

Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
contextual bandits with surrogate losses, focusing on regrets of the form
$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K}
\sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$, where $\calF$ contains score functions
$f = (f_1, \ldots, f_K)$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac
s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
information-theoretic regret upper bounds for various settings of $\calF$. On
the other hand, it gives an efficient algorithm with an $O(\sqrt{T})$ regret
against the benchmark of $\calF = \cbr{x \mapsto W x: W \in \R^{k \times d},
\one^T W = 0}$. A direct application of this result to \textsc{Online Bandit
Multiclass Linear Classification} gives an algorithm with $O(\sqrt{T})$ mistake
bound in the strongly linearly separable case.

### 2019-02-05 ICML-submission/title-and-abstract.tex
Update title-and-abstract.tex
Added a sentence on answering an open question in the Banditron paper
Removed the open problem reference from abstract
minor
a pass over the paper

\twocolumn[
\icmltitle{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}

@@

\item Under the more challenging weak linear separability condition, we design
an efficient algorithm with a mistake bound of $2^{\widetilde{O}(\min(K \log^2
(1/\gamma), \sqrt{1/\gamma} \log K))}$ \footnote{We use the notation
$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}. Our algorithm
is based on kernel Perceptron, which is inspired by the work
of \citet{Klivans-Servedio-2008} on improperly learning intersection of halfspaces.
%is based on a infinite-dimensional feature mapping that transforms weakly linear
%separable examples to strongly linear separable examples, which in turn is
%of \citet{Shalev-Shwartz-Shamir-Sridharan-2011},
\end{enumerate}
\end{abstract}

>>>>

\twocolumn[
\icmltitle{Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case}

@@

\item Under the more challenging weak linear separability condition, we design
an efficient algorithm with a mistake bound of $\min (2^{\widetilde{O}(K \log^2
(1/\gamma))}, 2^{\widetilde{O}(\sqrt{1/\gamma} \log K)})$ \footnote{We use the notation
$\widetilde{O}(f(\cdot)) = O(f(\cdot) \polylog(f(\cdot)))$.}.
Our algorithm
is based on kernel Perceptron, which is inspired by the work
of \citet{Klivans-Servedio-2008} on improperly learning intersection of halfspaces.
%is based on a infinite-dimensional feature mapping that transforms weakly linear
%separable examples to strongly linear separable examples, which in turn is
%of \citet{Shalev-Shwartz-Shamir-Sridharan-2011},
\end{enumerate}
\end{abstract}
